Non-intrusive reduced order modeling of nonlinear problems \\ using neural networks

### 2018-01-25 revision/RBMNN_manuscript_revised.tex
Add files for re-submission.

% Add line numbers
%\usepackage[modulo, displaymath, mathlines, running]{lineno}

@@

\begin{document}
	%\linenumbers

@@

		\begin{abstract}
			%\begin{linenumbers}
			We develop a non-intrusive reduced basis (RB) method for pa\-ra\-me\-tri\-zed steady-state partial differential equations (PDEs). The method extracts a reduced basis from a collection of high-fidelity solutions via a proper orthogonal decomposition (POD) and employs artificial neural networks (ANNs), particularly multi-layer perceptrons (MLPs), to accurately approximate the coefficients of the reduced model. The search for the optimal number of neurons and the minimum amount of training samples to avoid overfitting is carried out in the offline phase through an automatic routine, relying upon a joint use of the latin hypercube sampling (LHS) and the Levenberg-Marquardt (LM) training algorithm. This guarantees a complete offline-online decoupling, leading to an efficient RB method - referred to as POD-NN - suitable also for general nonlinear problems with a non-affine parametric dependence. Numerical studies are presented for the nonlinear Poisson equation and for driven cavity viscous flows, modeled through the steady incompressible Navier-Stokes equations. Both physical and geometrical parametrizations are considered. Several results confirm the accuracy of the POD-NN method and show the substantial speed-up enabled at the online stage as compared to a traditional RB strategy.		
			%\end{linenumbers}
		\end{abstract}

@@

		\emph{Reduced basis} (RB) methods constitute a well-known and widely-used example of reduced order modeling techniques. They are generally implemented pursuing an offline-online paradigm \cite{Mad06}. Based upon an ensemble of \emph{snapshots} (i.e., high-fidelity solutions to the parametrized differential problem), the goal of the \emph{offline} step is to construct a solution-dependent basis, yielding a reduced space of globally approximating functions to represent the main dynamics of the full-order model \cite{Bal14, Chen17}. For this, two major approaches have been proposed in the literature: proper orthogonal decomposition (POD) \cite{Lia02, Vol08} and greedy algorithms \cite{HSZ14}. The former relies on a deterministic or random sample in the parameter space to generate snapshots and then employs a singular value decomposition (SVD) to recover the reduced basis. In the second approach, the basis vectors coincide with the snapshots themselves, carefully selected according to some optimality criterion. As a result, a greedy strategy is typically more effective and efficient than POD, as it enables the exploration of a wider region of the parameter space while entailing the computation of many fewer high-fidelity solutions \cite{HSR16}. However, there exist problems for which a greedy approach is not feasible, simply because a natural criterion for the choice of the snapshots is not available \cite{Bal14}.

@@

		Consider a Hilbert space $\wt{V} = \wt{V}(\bg{\mu}_g) = \wt{V}(\wt{\Omega}(\boldsymbol{\mu}_g))$ defined over the domain $\wt{\Omega}(\boldsymbol{\mu}_g)$, equipped with the scalar product $(\cdot, \cdot)_{\wt{V}}$ and the induced norm $\norm{\cdot}_{\wt{V}} = \sqrt{(\cdot, \cdot)_{\wt{V}}}$. Furthermore, let $\wt{V}' = \wt{V}'(\boldsymbol{\mu}_g)$ be the dual space of $\wt{V}$. Denoting by $\wt{G} ~ : ~ \wt{V} \times \mathcal{P}_{ph} \rightarrow \wt{V}'$ the map representing a parametrized nonlinear second-order PDE, the differential (strong) form of the problem of interest reads: given $\bg{\mu} = (\bg{\mu}_{ph}, \, \bg{\mu}_g) \in \mathcal{P}$, find $\wt{u}(\boldsymbol{\mu}) \in \wt{V}(\bg{\mu}_g)$ such that
		%\begin{linenomath}
		\begin{equation}
			\label{eq:pde-differential-form}
			\wt{G}(\wt{u}(\bg{\mu}); \, \bg{\mu}_{ph}) = 0 \hspace*{0.3cm} \text{in $\wt{V}'(\bg{\mu}_g)$} \, ,
		\end{equation}
		%\end{linenomath}
		namely
		%\begin{linenomath}
		\begin{equation*}
			\langle \wt{G}(\wt{u}(\bg{\mu}); \, \bg{\mu}_{ph}), \, v \rangle_{\wt{V}',\wt{V}} = 0 \hspace*{0.3cm} \forall v \in \wt{V}(\bg{\mu}_g) \, ,
		\end{equation*}
		%\end{linenomath}
		with $\langle \cdot, \, \cdot \rangle_{\wt{V}',\wt{V}} ~ : ~ \wt{V}' \times \wt{V} \rightarrow \mathbb{R}$ the duality pairing between $\wt{V}'$ and $\wt{V}$.

		The finite element method requires problem \eqref{eq:pde-differential-form} to be stated in a weak (or variational) form \cite{Qua10}. To this end, let us introduce the form $\wt{g} ~ : ~ \wt{V} \times \wt{V} \times \mathcal{P} \rightarrow \mathbb{R}$, with $\wt{g}(\cdot, \, \cdot; \, \bg{\mu})$ defined as:
		%\begin{linenomath}
		\begin{equation*}
			\wt{g}(w, \, v; \, \bg{\mu}) = \langle \wt{G}(w; \, \bg{\mu}_{ph}), \, v \rangle_{\wt{V}',\wt{V}} \hspace*{0.3cm} \forall w, \, v \in \wt{V} \, .
		\end{equation*}
		%\end{linenomath}
		The variational formulation of \eqref{eq:pde-differential-form} then reads: given $\bg{\mu} = (\bg{\mu}_{ph}, \, \bg{\mu}_g) \in \mathcal{P}$, find $\wt{u}(\bg{\mu}) \in \wt{V}(\bg{\mu}_g)$ such that
		%\begin{linenomath}
		\begin{equation*}
			\wt{g}(\wt{u}(\bg{\mu}), \, v; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v \in \wt{V}(\bg{\mu}_g) \, .
		\end{equation*}
		%\end{linenomath}

@@

		As discussed in the Introduction, a reduced basis method seeks an approximated solution to a problem as a combination of (few) well-chosen basis vectors. These typically result from a suitable combination of a collection of high-fidelity approximations, called \emph{snapshots}. Therefore, when addressing problems defined on variable shape domains, ensuring the \emph{compatibility} among snapshots is crucial. To this end, it is practice to formulate and solve the differential problem over a fixed, \emph{parameter-independent} domain $\Omega \subset \mathbb{R}^d$ \cite{MN16}. This can be accomplished by introducing a parametrized map $\bg{\Phi} ~ : ~ \Omega \times \mathcal{P}_g \rightarrow \wt{\Omega}$ such that
		%\begin{linenomath}
		\begin{equation*}
			\wt{\Omega}(\bg{\mu}_g) = \bg{\Phi}(\Omega; \, \bg{\mu}_g) \, .
		\end{equation*}
		%\end{linenomath}
		The transformation $\bg{\Phi}(\cdot; \, \bg{\mu}_g)$ allows one to restate the general problem \eqref{eq:pde-differential-form}. Let $V$ be a suitable Hilbert space over $\Omega$ and $V'$ be its dual. Suppose $V$ is equipped with the scalar product $(\cdot, \cdot)_V$ and the induced norm $\norm{\cdot}_V = \sqrt{(\cdot, \cdot)_V}$. Given the parametrized map $G ~ : V \times \mathcal{P} \rightarrow V'$ representing the (nonlinear) PDE over the reference domain $\Omega$, we focus on problems of the form: given $\bg{\mu} \in \mathcal{P}$, find $u(\bg{\mu}) \in V$ such that
		%\begin{linenomath}
		\begin{equation}
			\label{eq:pde-differential-reference}
			G(u(\bg{\mu}); \, \bg{\mu}) = 0 \hspace*{0.3cm} \text{in $V'$} \, .
		\end{equation}
		%\end{linenomath}
		The weak formulation of problem \eqref{eq:pde-differential-reference} reads: given $\bg{\mu} \in \mathcal{P}$, seek $u(\bg{\mu}) \in V$ such that
		%\begin{linenomath}
		\begin{equation}
			\label{eq:pde-weak-reference}
			g(u(\bg{\mu}), \, v; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v \in V \, ,
		\end{equation}
		%\end{linenomath}
		where $g ~ : ~ V \times V \times \mathcal{P} \rightarrow \mathbb{R}$ is defined as
		%\begin{linenomath}
		\begin{equation*}
			g(w, \, v; \, \bg{\mu}) = \langle G(w; \, \bg{\mu}), \, v \rangle_{V',V} \hspace*{0.3cm} \forall w, \, v \in V \, , ~ \forall \bg{\mu} \in \mathcal{P} \, ,
		\end{equation*}
		%\end{linenomath}
		with $\langle \cdot, \, \cdot \rangle_{V',V} ~ : ~ V' \times V \rightarrow \mathbb{R}$ the dual pairing between $V$ and $V'$. Observe that the explicit expression of $g(\cdot, \, \cdot; \, \bg{\mu})$ involves the map $\bg{\Phi}(\cdot; \, \bg{\mu}_g)$, thus keeping track of the original domain $\wt{\Omega}(\bg{\mu}_g)$. Then, the solution $\wt{u}(\bg{\mu})$ over the original domain $\wt{\Omega}(\bg{\mu}_g)$ can be recovered as
		%\begin{linenomath}
		\begin{equation*}
			\wt{u}(\bg{\mu}) = u(\bg{\mu}) \circ \bg{\Phi}(\bg{\mu}_g) \, .
		\end{equation*}
		%\end{linenomath}
		In our numerical tests, we employ the squared reference domain shown on the right in Fig. \ref{fig:poisson2d-fig1} and we resort to a particular choice for $\bg{\Phi}(\cdot; \, \bg{\mu}_g)$ - the boundary displacement-dependent transfinite map (BDD TM) proposed by Jaggli \emph{et al}. \cite{JIR14}.

@@

		Let $V_h \subset V$ be a suitable FE subspace of $V$ of (finite) dimension $N_h$, with $h \geq 0$ being the characteristic size of the underlying mesh $\Omega_h$ which discretizes $\Omega$. The FE approximation of the weak problem \eqref{eq:pde-weak-reference} can be cast in the form: given $\bg{\mu} \in \mathcal{P}$, find $u_h(\bg{\mu}) \in V_h$ such that 
		%\begin{linenomath}
		\begin{equation}
			\label{eq:galerkin}
			g(u_h(\bg{\mu}), \, v_h; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v_h \in V_h \, .
		\end{equation}
		%\end{linenomath}
		From an algebraic standpoint, letting $\big\lbrace \phi_1, \, \ldots \, , \phi_{N_h} \big\rbrace$ be a Lagrangian basis for $V_h$ and denoting by $\mathbf{u}_h(\bg{\mu}) \in \mathbb{R}^{N_h}$ the vector collecting the \emph{nodal values} $\big\lbrace u_h^{(1)}(\bg{\mu}), \, \ldots \, , u_h^{(N_h)}(\bg{\mu}) \big\rbrace$ of $u_h(\bg{\mu})$, problem \eqref{eq:galerkin} is equivalent to: given $\bg{\mu} \in \mathcal{P}$, find $\mathbf{u}_h(\bg{\mu}) \in \mathbb{R}^{N_h}$ such that
		%\begin{linenomath}
		\begin{equation}
			\label{eq:galerkin-algebraic}
			\mathbf{G}_h(\mathbf{u}_h(\bg{\mu}); \, \bg{\mu}) = \mathbf{0} \in \mathbb{R}^{N_h} \, ,
		\end{equation}
		%\end{linenomath}
		where the $i$-th component of the \emph{residual vector} $\mathbf{G}_h(\cdot; \, \bg{\mu})$ is given by
		%\begin{linenomath}
		\begin{equation}
			\label{eq:galerkin-algebraic-component}
			\big( \mathbf{G}_h(\mathbf{u}_h(\bg{\mu}); \, \bg{\mu}) \big)_i = g(u_h(\bg{\mu}), \, \phi_i; \, \bg{\mu}) \, , \hspace*{0.3cm} i = 1, \, \ldots \, , N_h \, .
		\end{equation}
		%\end{linenomath}
		Observe that, due to the nonlinearity of $g(\cdot, \, \cdot; \, \bg{\mu})$ in its first argument, one has to resort to some iterative method, e.g., Newton's method, to solve the \emph{Galerkin} problem \eqref{eq:galerkin-algebraic}.

@@

		%\begin{linenomath}
		\begin{equation*}

@@

		\end{equation*}
		%\end{linenomath} 

@@

		%\begin{linenomath}
		\begin{equation}

@@

		\end{equation}
		%\end{linenomath}

@@

		%\begin{linenomath}
		\begin{equation*}

@@

		%\begin{linenomath}
		\begin{equation}

@@

		\end{equation}
		%\end{linenomath}

@@

		An artificial neuron $j$ is completely characterized by three functions: the propagation function, the activation function and the output function. The \emph{propagation function} $f_{prop}$ converts the vectorial input $\mathbf{p} = [y_{s_1}, \, \ldots \, , y_{s_m}]^T \in \mathbb{R}^m$ into a scalar $u_{j}$ often called \emph{net input}, i.e.,
		%\begin{linenomath}
		\begin{equation*}
			u_{j} = f_{prop}(w_{s_1,j}, \, \ldots \, , w_{s_m,j}, \, y_{s_1}, \, \ldots \, , y_{s_m}) \, .
		\end{equation*}
		%\end{linenomath}
		A common choice for $f_{prop}$ (used also in this work) is the weighted sum, adding up the scalar inputs multiplied by their respective weights:
		%\begin{linenomath}
		\begin{equation*}
			f_{prop}(w_{s_1,j}, \, \ldots \, , w_{s_m,j}, \, y_{s_1}, \, \ldots \, , y_{s_m}) = \sum_{k = 1}^m w_{s_k,j} ~ y_{s_k} \, .
		\end{equation*}
		%\end{linenomath} 
		At each timestep, the \emph{activation state} $a_j$, often referred to as \emph{activation}, quantifies to which extent neuron $j$ is currently \emph{active} or \emph{excited}. It results from the \emph{activation function} $f_{act}$, which combines the net input $u_j$ with a threshold $\theta_j \in \mathbb{R}$ \cite{Kri07}: 
		%\begin{linenomath}
		\begin{equation*}
			a_j = f_{act}(u_j; \, \theta_j) = f_{act} \big( \sum_{k = 1}^m w_{s_k,j} ~ y_{s_k} \, ; \, \theta_j \big) \, .
		\end{equation*}
		%\end{linenomath}
		Note that the threshold $\theta_j$ is a parameter of the network and as such one may choose to adapt it through a training process, exactly as it can be done for the synaptic weights. To ease the runtime access of $\theta_j$, it is common practice to introduce a \emph{bias neuron} in the network. A bias neuron is a continuously firing neuron, with constant output $y_{b} = 1$, which is directly connected with neuron $j$, assigning the \emph{bias weight} $w_{b,j} = - \theta_j$ to the connection. As can be deduced by the representation on the right in Fig. \ref{fig:neural-model}, $\theta_j$ is now treated as a synaptic weight, while the neuron threshold is set to zero. Therefore, the net input and the activation state can respectively be expressed as
		%\begin{linenomath}
		\begin{equation*}
			u_j = \sum_{k = 1}^m w_{s_k,j} ~ y_{s_k} - \, \theta_j \hspace*{0.5cm} \text{and} \hspace*{0.5cm} a_j = f_{act} \big( \sum_{k = 1}^m w_{s_k,j} ~ y_{s_k} - \, \theta_j \big) \, .
		\end{equation*}
		%\end{linenomath}		
		There exist various choices for the activation function. The sigmoid activation functions have been widely used for the realization of artificial neural networks due to their graceful combination of linear and nonlinear behaviour \cite{Hay05}. Sigmoid functions are s-shaped, monotically increasing, and assume values in a bounded interval; a well-known instance is given by the hyperbolic tangent,
		%\begin{linenomath}
		\begin{equation*}
			f_{act}(v) = \dfrac{e^{v} - e^{-v}}{e^v + e^{-v}} \, .
		\end{equation*}
		%\end{linenomath}
		Finally, the \emph{output function} $f_{out}$ calculates the scalar \emph{output} $y_j \in \mathbb{R}$ based on the activation state $a_j$ of the neuron:
		%\begin{linenomath}
		\begin{equation*}
			y_j = f_{out}(a_j) \, .
		\end{equation*}
		%\end{linenomath} 
		Often, $f_{out}$ is the identity function, so that activation and output of a neuron coincides, i.e., $y_j = f_{out}(a_j) = a_j$. The output $y_j$ could then be sent either to other neurons or constitute a component of the overall output vector of the network, as for the neurons in the output layer of a feedforward neural network, illustrated in the following subsection.

		It should be pointed out that the neural model presented so far refers to the so called \emph{computing} neuron, i.e., a neuron which processes input information to provide a response. However, in a neural network one may also identify \emph{source} neurons, supplying the network with the respective components of the input vector, without performing any computation \cite{Hay05}.

@@

		As previously mentioned, the principal characteristic of a neural network is its capability of \emph{learning} from the surrounding environment, storing the acquired knowledge via its internal parameters, i.e., the synaptic and bias weights. Learning is accomplished through a training process, during which the network is exposed to a collection of examples, called \emph{training data}. According to some performance measure, the weights are then adjusted by means of a well-defined set of rules. Therefore, the learning procedure is an \emph{algorithm}, typically iterative, such that after a successfull training, the neural network provides reasonable responses for unknown problems of the same class of the training set. This property is known as \emph{generalization} \cite{Kri07}.

		Training algorithms can be classified based on the nature of the training set, i.e., the set of training data. We can then distinguish three \emph{learning paradigms}: supervised learning, unsupervised learning and reinforcement learning \cite{Hag96}. The choice of the learning paradigm is clearly task-dependent. Particularly, for function approximation, the \emph{supervised} learning paradigm is the natural choice.

>>>>

% Add line numbers
\usepackage[modulo, displaymath, mathlines, running]{lineno}

@@

\begin{document}
	\linenumbers

@@

		\begin{abstract}
			\begin{linenumbers}
			We develop a non-intrusive reduced basis (RB) method for pa\-ra\-me\-tri\-zed steady-state partial differential equations (PDEs). The method extracts a reduced basis from a collection of high-fidelity solutions via a proper orthogonal decomposition (POD) and employs artificial neural networks (ANNs), particularly multi-layer perceptrons (MLPs), to accurately approximate the coefficients of the reduced model. The search for the optimal number of neurons and the minimum amount of training samples to avoid overfitting is carried out in the offline phase through an automatic routine, relying upon a joint use of the latin hypercube sampling (LHS) and the Levenberg-Marquardt (\textcolor{deepgreen}{LM}) training algorithm. This guarantees a complete offline-online decoupling, leading to an efficient RB method - referred to as POD-NN - suitable also for general nonlinear problems with a non-affine parametric dependence. Numerical studies are presented for the nonlinear Poisson equation and for driven cavity viscous flows, modeled through the steady incompressible Navier-Stokes equations. Both physical and geometrical parametrizations are considered. Several results confirm the accuracy of the POD-NN method and show the substantial speed-up enabled at the online stage as compared to a traditional RB strategy.		
			\end{linenumbers}
		\end{abstract}

@@

		\emph{Reduced basis} (RB) methods constitute a well-known and widely-used example of reduced order modeling techniques. They are generally implemented pursuing an offline-online paradigm \cite{Mad06}. Based upon an ensemble of \emph{snapshots} (i.e., high-fidelity solutions to the parametrized differential problem), the goal of the \emph{offline} step is to construct a solution-dependent basis, yielding a reduced space of globally approximating functions to represent the main dynamics of the full-order model \cite{Bal14, Chen17}. For this, two major approaches have been proposed in the literature: proper orthogonal decomposition (POD) \cite{Lia02, Vol08} and greedy algorithms \cite{HSZ14}. The former relies on a deterministic or random sample in the parameter space to{\linebreak\clearpage\noindent}generate snapshots and then employs a singular value decomposition (SVD) to recover the reduced basis. In the second approach, the basis vectors coincide with the snapshots themselves, carefully selected according to some optimality criterion. As a result, a greedy strategy is typically more effective and efficient than POD, as it enables the exploration of a wider region of the parameter space while entailing the computation of many fewer high-fidelity solutions \cite{HSR16}. However, there exist problems for which a greedy approach is not feasible, simply because a natural criterion for the choice of the snapshots is not available \cite{Bal14}.

@@

		Consider a Hilbert space $\wt{V} = \wt{V}(\bg{\mu}_g) = \wt{V}(\wt{\Omega}(\boldsymbol{\mu}_g))$ defined over the domain $\wt{\Omega}(\boldsymbol{\mu}_g)$, equipped with the scalar product $(\cdot, \cdot)_{\wt{V}}$ and the induced norm $\norm{\cdot}_{\wt{V}} = \sqrt{(\cdot, \cdot)_{\wt{V}}}$. Furthermore, let $\wt{V}' = \wt{V}'(\boldsymbol{\mu}_g)$ be the dual space of $\wt{V}$. Denoting by $\wt{G} ~ : ~ \wt{V} \times \mathcal{P}_{ph} \rightarrow \wt{V}'$ the map representing a parametrized nonlinear second-order PDE, the differential (strong) form of the problem of interest reads: given $\bg{\mu} = (\bg{\mu}_{ph}, \, \bg{\mu}_g) \in \mathcal{P}$, find $\wt{u}(\boldsymbol{\mu}) \in \wt{V}(\bg{\mu}_g)$ such that
		\begin{linenomath}\begin{equation}
			\label{eq:pde-differential-form}
			\wt{G}(\wt{u}(\bg{\mu}); \, \bg{\mu}_{ph}) = 0 \hspace*{0.3cm} \text{in $\wt{V}'(\bg{\mu}_g)$} \, ,
		\end{equation}\end{linenomath}
		namely
		\begin{linenomath}\begin{linenomath}\begin{equation*}
			\langle \wt{G}(\wt{u}(\bg{\mu}); \, \bg{\mu}_{ph}), \, v \rangle_{\wt{V}',\wt{V}} = 0 \hspace*{0.3cm} \forall v \in \wt{V}(\bg{\mu}_g) \, ,
		\end{equation*}\end{linenomath}\end{linenomath}
		with $\langle \cdot, \, \cdot \rangle_{\wt{V}',\wt{V}} ~ : ~ \wt{V}' \times \wt{V} \rightarrow \mathbb{R}$ the duality pairing between $\wt{V}'$ and $\wt{V}$.

		The finite element method requires problem \eqref{eq:pde-differential-form} to be stated in a weak (or variational) form \cite{Qua10}. To this end, let us introduce the form $\wt{g} ~ : ~ \wt{V} \times \wt{V} \times \mathcal{P} \rightarrow \mathbb{R}$, with $\wt{g}(\cdot, \, \cdot; \, \bg{\mu})$ defined as:
		\begin{linenomath}\begin{linenomath}\begin{equation*}
			\wt{g}(w, \, v; \, \bg{\mu}) = \langle \wt{G}(w; \, \bg{\mu}_{ph}), \, v \rangle_{\wt{V}',\wt{V}} \hspace*{0.3cm} \forall w, \, v \in \wt{V} \, .
		\end{equation*}\end{linenomath}\end{linenomath}
		The variational formulation of \eqref{eq:pde-differential-form} then reads: given $\bg{\mu} = (\bg{\mu}_{ph}, \, \bg{\mu}_g) \in \mathcal{P}$, find $\wt{u}(\bg{\mu}) \in \wt{V}(\bg{\mu}_g)$ such that
		\begin{linenomath}\begin{equation*}
			\wt{g}(\wt{u}(\bg{\mu}), \, v; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v \in \wt{V}(\bg{\mu}_g) \, .
		\end{equation*}\end{linenomath}

@@

		As discussed in the Introduction, a reduced basis method seeks an approximated solution to a problem as a combination of (few) well-chosen basis vectors. These typically result from a suitable combination of a collection of high-fidelity approximations, called \emph{snapshots}. Therefore, when addressing problems defined on variable shape domains, ensuring the \emph{compatibility} among snapshots is crucial. To this end, it is practice to formulate and solve the differential problem over a fixed, \emph{parameter-independent} domain $\Omega \subset \mathbb{R}^d$ \cite{MN16}. This can be accomplished by introducing a parametrized map $\bg{\Phi} ~ : ~ \Omega \times \mathcal{P}_g \rightarrow \wt{\Omega}$ such that
		\begin{linenomath}\begin{linenomath}\begin{equation*}
			\wt{\Omega}(\bg{\mu}_g) = \bg{\Phi}(\Omega; \, \bg{\mu}_g) \, .
		\end{equation*}\end{linenomath}\end{linenomath}
		The transformation $\bg{\Phi}(\cdot; \, \bg{\mu}_g)$ allows one to restate the general problem \eqref{eq:pde-differential-form}. Let $V$ be a suitable Hilbert space over $\Omega$ and $V'$ be its dual. Suppose $V$ is equipped with the scalar product $(\cdot, \cdot)_V$ and the induced norm $\norm{\cdot}_V = \sqrt{(\cdot, \cdot)_V}$. Given the parametrized map $G ~ : V \times \mathcal{P} \rightarrow V'$ representing the (nonlinear) PDE over the reference domain $\Omega$, we focus on problems of the form: given $\bg{\mu} \in \mathcal{P}$, find $u(\bg{\mu}) \in V$ such that
		\begin{linenomath}\begin{linenomath}\begin{equation}
			\label{eq:pde-differential-reference}
			G(u(\bg{\mu}); \, \bg{\mu}) = 0 \hspace*{0.3cm} \text{in $V'$} \, .
		\end{equation}\end{linenomath}\end{linenomath}
		The weak formulation of problem \eqref{eq:pde-differential-reference} reads: given $\bg{\mu} \in \mathcal{P}$, seek $u(\bg{\mu}) \in V$ such that
		\begin{linenomath}\begin{linenomath}\begin{equation}
			\label{eq:pde-weak-reference}
			g(u(\bg{\mu}), \, v; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v \in V \, ,
		\end{equation}\end{linenomath}\end{linenomath}
		where $g ~ : ~ V \times V \times \mathcal{P} \rightarrow \mathbb{R}$ is defined as
		\begin{linenomath}\begin{linenomath}\begin{equation*}
			g(w, \, v; \, \bg{\mu}) = \langle G(w; \, \bg{\mu}), \, v \rangle_{V',V} \hspace*{0.3cm} \forall w, \, v \in V \, , ~ \forall \bg{\mu} \in \mathcal{P} \, ,
		\end{equation*}\end{linenomath}\end{linenomath}
		with $\langle \cdot, \, \cdot \rangle_{V',V} ~ : ~ V' \times V \rightarrow \mathbb{R}$ the dual pairing between $V$ and $V'$. Observe that the explicit expression of $g(\cdot, \, \cdot; \, \bg{\mu})$ involves the map $\bg{\Phi}(\cdot; \, \bg{\mu}_g)$, thus keeping track of the original domain $\wt{\Omega}(\bg{\mu}_g)$. Then, the solution $\wt{u}(\bg{\mu})$ over the original domain $\wt{\Omega}(\bg{\mu}_g)$ can be recovered as
		\begin{linenomath}\begin{linenomath}\begin{equation*}
			\wt{u}(\bg{\mu}) = u(\bg{\mu}) \circ \bg{\Phi}(\bg{\mu}_g) \, .
		\end{equation*}\end{linenomath}\end{linenomath}
		In our numerical tests, we employ the squared reference domain shown on the right in Fig. \ref{fig:poisson2d-fig1} and we resort to a particular choice for $\bg{\Phi}(\cdot; \, \bg{\mu}_g)$ - the boundary displacement-dependent transfinite map (BDD TM) proposed by Jaggli \emph{et al}. \cite{JIR14}.

@@

		Let $V_h \subset V$ be a suitable FE subspace of $V$ of (finite) dimension $N_h$, with $h \geq 0$ being the characteristic size of the underlying mesh $\Omega_h$ which discretizes $\Omega$. The FE approximation of the weak problem \eqref{eq:pde-weak-reference} can be cast in the form: given $\bg{\mu} \in \mathcal{P}$, find $u_h(\bg{\mu}) \in V_h$ such that 
		\begin{linenomath}\begin{linenomath}\begin{equation}
			\label{eq:galerkin}
			g(u_h(\bg{\mu}), \, v_h; \, \bg{\mu}) = 0 \hspace*{0.3cm} \forall v_h \in V_h \, .
		\end{equation}\end{linenomath}\end{linenomath}
		From an algebraic standpoint, letting $\big\lbrace \phi_1, \, \ldots \, , \phi_{N_h} \big\rbrace$ be a Lagrangian basis for $V_h$ and denoting by $\mathbf{u}_h(\bg{\mu}) \in \mathbb{R}^{N_h}$ the vector collecting the \emph{nodal values} $\big\lbrace u_h^{(1)}(\bg{\mu}), \, \ldots \, , u_h^{(N_h)}(\bg{\mu}) \big\rbrace$ of $u_h(\bg{\mu})$, problem \eqref{eq:galerkin} is equivalent to: given $\bg{\mu} \in \mathcal{P}$, find $\mathbf{u}_h(\bg{\mu}) \in \mathbb{R}^{N_h}$ such that
		\begin{linenomath}\begin{linenomath}\begin{equation}
			\label{eq:galerkin-algebraic}
			\mathbf{G}_h(\mathbf{u}_h(\bg{\mu}); \, \bg{\mu}) = \mathbf{0} \in \mathbb{R}^{N_h} \, ,
		\end{equation}\end{linenomath}\end{linenomath}
		where the $i$-th component of the \emph{residual vector} $\mathbf{G}_h(\cdot; \, \bg{\mu})$ is given by
		\begin{linenomath}\begin{linenomath}\begin{equation}
			\label{eq:galerkin-algebraic-component}
			\big( \mathbf{G}_h(\mathbf{u}_h(\bg{\mu}); \, \bg{\mu}) \big)_i = g(u_h(\bg{\mu}), \, \phi_i; \, \bg{\mu}) \, , \hspace*{0.3cm} i = 1, \, \ldots \, , N_h \, .
		\end{equation}\end{linenomath}\end{linenomath}
		Observe that, due to the nonlinearity of $g(\cdot, \, \cdot; \, \bg{\mu})$ in its first argument, one has to resort to some iterative method, e.g., Newton's method, to solve the \emph{Galerkin} problem \eqref{eq:galerkin-algebraic}.

@@

		\begin{linenomath}\begin{equation*}

@@

		\end{equation*}\end{linenomath} 

@@

		\begin{linenomath}\begin{linenomath}\begin{equation}

@@

		\end{equation}\end{linenomath}\end{linenomath}

@@

		\begin{linenomath}\begin{equation*}
			\label{eq:svd}

@@

		\begin{linenomath}\begin{equation}

@@

		\end{equation}\end{linenomath}

@@

		An artificial neuron $j$ is completely characterized by three functions: the propagation function, the activation function and the output function. The \emph{propagation function} $f_{prop}$ converts the vectorial input $\mathbf{p} = [y_{s_1}, \, \ldots \, , y_{s_m}]^T \in \mathbb{R}^m$ into a scalar $u_{j}$ often called \emph{net input}, i.e.,
		\begin{linenomath}\begin{equation*}
			u_{j} = f_{prop}(w_{s_1,j}, \, \ldots \, , w_{s_m,j}, \, y_{s_1}, \, \ldots \, , y_{s_m}) \, .
		\end{equation*}\end{linenomath}
		A common choice for $f_{prop}$ (used also in this work) is the weighted sum, adding up the scalar inputs multiplied by their respective weights:
		\begin{linenomath}\begin{equation*}
			f_{prop}(w_{s_1,j}, \, \ldots \, , w_{s_m,j}, \, y_{s_1}, \, \ldots \, , y_{s_m}) = \sum_{k = 1}^m w_{s_k,j} ~ y_{s_k} \, .
		\end{equation*}\end{linenomath} 
		At each timestep, the \emph{activation state} $a_j$, often referred to as \emph{activation}, quantifies to which extent neuron $j$ is currently \emph{active} or \emph{excited}. It results from the \emph{activation function} $f_{act}$, which combines the net input $u_j$ with a threshold $\theta_j \in \mathbb{R}$ \cite{Kri07}: 
		\begin{linenomath}\begin{equation*}
			a_j = f_{act}(u_j; \, \theta_j) = f_{act} \big( \sum_{k = 1}^m w_{s_k,j} ~ y_{s_k} \, ; \, \theta_j \big) \, .
		\end{equation*}\end{linenomath}
		Note that the threshold $\theta_j$ is a parameter of the network and as such one may choose to adapt it through a training process, exactly as it can be done for the synaptic weights. To ease the runtime access of $\theta_j$, it is common practice to introduce a \emph{bias neuron} in the network. A bias neuron is a continuously firing neuron, with constant output $y_{b} = 1$, which is directly connected with neuron $j$, assigning the \emph{bias weight} $w_{b,j} = - \theta_j$ to the connection. As can be deduced by the representation on the right in Fig. \ref{fig:neural-model}, $\theta_j$ is now treated as a synaptic weight, while the neuron threshold is set to zero. Therefore, the net input and the activation state can respectively be expressed as
		\begin{linenomath}\begin{equation*}
			u_j = \sum_{k = 1}^m w_{s_k,j} ~ y_{s_k} - \, \theta_j \hspace*{0.5cm} \text{and} \hspace*{0.5cm} a_j = f_{act} \big( \sum_{k = 1}^m w_{s_k,j} ~ y_{s_k} - \, \theta_j \big) \, .
		\end{equation*}\end{linenomath}		
		There exist various choices for the activation function. The sigmoid activation functions have been widely used for the realization of artificial neural networks due to their graceful combination of linear and nonlinear behaviour \cite{Hay05}. Sigmoid functions are s-shaped, monotically increasing, and assume values in a bounded interval; a well-known instance is given by the hyperbolic tangent,
		\begin{linenomath}\begin{equation*}
			f_{act}(v) = \dfrac{e^{v} - e^{-v}}{e^v + e^{-v}} \, .
		\end{equation*}\end{linenomath}
		Finally, the \emph{output function} $f_{out}$ calculates the scalar \emph{output} $y_j \in \mathbb{R}$ based on the activation state $a_j$ of the neuron:
		\begin{linenomath}\begin{equation*}
			y_j = f_{out}(a_j) \, .
		\end{equation*}\end{linenomath} 
		Often, $f_{out}$ is the identity function, so that activation and output of a neuron coincides, i.e., $y_j = f_{out}(a_j) = a_j$. The output $y_j$ could then be sent either to other neurons or constitute a component of the overall output vector of the network, as for the neurons in the output layer of a feedforward neural network, illustrated in the following subsection.

		It should be pointed out that the neural model presented so far refers to the so called \emph{computing} neuron, i.e., a neuron which processes input information to provide a response. However, in a neural network one may also identify \emph{source} neurons, supplying the network with the respective components of the \textcolor{red}{input vector}, without performing any computation \cite{Hay05}.

@@

		As previously mentioned, the principal characteristic of a neural network is its capability of \emph{learning} from the surrounding environment, storing the acquired knowledge via its internal parameters, i.e., the synaptic and bias weights. Learning is accomplished through a training process, during which the network is exposed to a collection of examples, called \textcolor{red}{\emph{training data}}. According to some performance measure, the weights are then adjusted by means of a well-defined set of rules. Therefore, the learning procedure is an \emph{algorithm}, typically iterative, such that after a successfull training, the neural network provides reasonable responses for unknown problems of the same class of the training set. This property is known as \emph{generalization} \cite{Kri07}.

		Training algorithms can be classified based on the nature of the training set, i.e., the set of \textcolor{red}{training data}. We can then distinguish three \emph{learning paradigms}: supervised learning, unsupervised learning and reinforcement learning \cite{Hag96}. The choice of the learning paradigm is clearly task-dependent. Particularly, for function approximation, the \emph{supervised} learning paradigm is the natural choice.
